Master's Project Journal

### 2019-04-10 thesis/FPGABasedADPLLs.tex
error combiner

Accordingly any intended error combiner design implementing an average should also be reconfigurable to satisfy the reconfigurability constraint.

>>>>

Accordingly any intended error combiner design implementing an average should also be reconfigurable to satisfy the reconfigurability constraint. Given this is a digital system the most straightforward way to implement this is as a weighted sum, followed by a division. The final \ac{ADPLL} network will be laid out in a Cartesian grid so a maximum of four values will possibly be combined, with only the non-corner edge nodes having a number of neighbours that is not a power of two.
The simplest, and most processing time efficient, method of calculating the weighted sum restricts the weights to powers of two, as this permits their implementation as a left bit shift which is trivially achieved in hardware by a part select.
Similarly this reasoning can be expanded to the division, where the complicated division by three for a non-corner edge node is instead replaced by division by four. This means the division is implemented identically by all error combiners in the network, and implemented trivially by a right shift of two bits.%TODO ask pierre re 3 div 4
